---
title: "Mapbiomas Data"
author: "Shai Vaz"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(tidyr)
library(tidyr)
library(stringr)
library(readxl)

# Datatable
library(data.table)
library(dtplyr)

# Geographic
library(sf)
library(datazoom.amazonia)

# Personal functions
source("../Functions/bulk_rds.R")
```

# Importing data

I'll extract the land cover and transitions data from MapBiomas through the Datazoom package. They present data from Collection 8, and it's already treated. 

## Land cover

```{r}
land_cover <- load_mapbiomas(
  dataset = "mapbiomas_cover",
  raw_data = FALSE,
  geo_level = "municipality",
  language = "eng"
  ) |> 
  as.data.table()
```

## Transition matrices

```{r}
transition <- load_mapbiomas(
  dataset = "mapbiomas_transition",
  raw_data = FALSE,
  geo_level = "municipality",
  language = "eng"
  ) |> 
  as.data.table()
```

# Cleaning data

## Clean Land cover

I will aggregate the data by land use, since I only need data for more aggregate levels. 

```{r}
land_cover_summarised <- land_cover |> 
  mutate(
    land_use = case_when(
      # forest 
      level_1 == "1. Forest" ~ "forest",
      # non-forest natural formation
      level_1 == "2. Non Forest Natural Formation" ~ "non_forest",
      # Agriculture
      level_2 == "Agriculture" ~ "agriculture",
      # Pasture
      level_2 == "Pasture" ~ "pasture",
      # Other
      .default = "other"
    )
  ) |> 
  # group by municipality - year - land use
  group_by(
    municipality_code,
    municipality_state,
    year,
    land_use
  ) |>
  # aggregate
  summarise(
    .groups = "keep",
    area = sum(value, na.rm = T)
  ) |> 
  ungroup(
    
  ) |> 
  # standard variable name
  mutate(
    code_muni = as.character(municipality_code),
    .before = "municipality_state",
    municipality_code = NULL
  ) 
```

## Clean transitions

```{r}
transition_summarised <- transition |> 
  mutate(
    # LAND USE TO
    to_land_use = case_when(
      # forest 
      to_level_1 == "1. Forest" ~ "forest",
      # non-forest natural formation
      to_level_1 == "2. Non Forest Natural Formation" ~ "non_forest",
      # Agriculture
      to_level_2 == "Agriculture" ~ "agriculture",
      # Pasture
      to_level_2 == "Pasture" ~ "pasture",
      # Other
      .default = "other"
    ),
    
    # LAND USE FROM
    from_land_use = case_when(
      # forest 
      from_level_1 == "1. Forest" ~ "forest",
      # non-forest natural formation
      from_level_1 == "2. Non Forest Natural Formation" ~ "non_forest",
      # Agriculture
      from_level_2 == "Agriculture" ~ "agriculture",
      # Pasture
      from_level_2 == "Pasture" ~ "pasture",
      # Other
      .default = "other"
    ),
    
    # YEAR FROM
    year_from = as.numeric(
      str_split_i(year, "_", 1)
      ),
    # YEAR TO
    year_to = as.numeric(
      str_split_i(year, "_", 2)
      )
  ) |> 
  # Select transitions from consecutive years
  filter(
   year_to == year_from + 1 
  ) |> 
  # group by municipality - year to and from - land uses to and from 
  group_by(
    municipality_code,
    municipality_state,
    year_from, year_to,
    from_land_use, to_land_use
  ) |>
  # aggregate
  summarise(
    .groups = "keep",
    value = sum(value, na.rm = T)
  ) |> 
  ungroup(
    
  ) |> 
  # standard variable name
  mutate(
    code_muni = as.character(municipality_code),
    .before = "municipality_state",
    municipality_code = NULL
  ) 
```

# Agregate by AMC

## Land cover

Now I aggregate the land cover data by AMC.

```{r}
land_cover_by_amc_long <- left_join(
  # land cover by municipality
  land_cover_summarised ,
  
  # municipality to amc translator
  muni_to_amc |> 
   select(
     code_amc,
     code_muni
   ),
  
  by = "code_muni"
  ) |> 
  # Group by amc - year - land use
  group_by(
    code_amc,
    year,
    land_use
  ) |> 
  # Aggregate
  summarise(
    .groups = "keep",
    area = sum(area, na.rm = T)
  ) |> 
  ungroup()
```

### Wide version

And I make a wide version, which will be the main data used.

```{r}
land_cover_by_amc <- land_cover_by_amc_long |> 
  pivot_wider(
    id_cols = c(code_amc, year),
    names_from = land_use,
    values_from = area
  )
```

## Transitions

```{r}
transition_by_amc_long <- left_join(
  # land cover by municipality
  transition_summarised ,
  
  # municipality to amc translator
  muni_to_amc |> 
   select(
     code_amc,
     code_muni
   ),
  
  by = "code_muni"
  ) |> 
  # Group by amc - year - land use
  group_by(
    code_amc,
    year_from, year_to,
    from_land_use, to_land_use
  ) |> 
  # Aggregate
  summarise(
    .groups = "keep",
    value = sum(value, na.rm = T)
  ) |> 
  ungroup(
    
  ) |> 
  # calculate conversion probabilities
  mutate(
    # grouping by AMC - year - from_land_use
    .by = c(code_amc, year_from, year_to, from_land_use),
    
    # probability of conversion TO each land use
    prob = value / sum(value, na.rm = T)
  )
```

### Wide version

I'll also make a wide version of the transition data.


```{r}
transition_by_amc <- transition_by_amc_long |>
  rename(
    from = from_land_use,
    to = to_land_use
  ) |> 
  pivot_wider(
    id_cols = c(code_amc, year_from, year_to),
    
    names_from = c(from, to),
    
    values_from = prob,
    
    names_sort = TRUE
  )
```

# Save as RDS

```{r}
bulk_write_rds(
  # raw
  land_cover,
  transition,
  # summarised
  land_cover_summarised,
  transition_summarised,
  # by amc
  land_cover_by_amc_long,
  land_cover_by_amc,
  
  transition_by_amc_long,
  transition_by_amc
)
```

