---
title: "Transportation Costs"
author: "Shai Vaz"
date: "May 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(readxl)

# Graphics
library(ggplot2)

# Geographic
library(sf)
library(terra)
```

# Importing

## Transportation Costs

```{r}
transport_cost <- rast(
  x = "../Inputs/cost_raster_raster_proj.tif"
  )
```

## Municipality Seats

```{r}
municipalities_tc <- read_rds(
  file = "../Variables/municipalities.rds"
  ) %>%
  # match crs with raster
  st_transform(
    crs(transport_cost)
  ) %>%
  # save with terra
  vect()
```

## Conservation Units

There are two groups of Conservation Units. Integral Protection (PI) areas have the objective of preserving nature, with only the indirect use of its natural resources being permitted. Sustainable Use (US) areas have the aim of reconciling nature conservation with sustainable use of natural resources. 

```{r}
conservation_units_tc <- read_rds(
  file = "../Variables/conservation_units.rds"
  ) %>%
  # filter only Integral Protection
  filter(
    group == "PI"
  ) %>% 
  # match crs with raster
  st_transform(
    crs(transport_cost)
  ) %>%
  # save with terra
  vect()
```


## Indigenous Lands

```{r}
indigenous_lands_tc <- read_rds(
  file = "../Variables/indigenous_lands.rds"
  ) %>%
  # match crs with raster
  st_transform(
    crs(transport_cost)
  ) %>%
  # save with terra
  vect()
```

# Transportation costs per municipality

## Removing protected areas

Here I'll remove conservation units and indigenous lands from the cost raster.

```{r}
transport_cost_unprotected <- transport_cost %>% 
  # cut conservation units
  mask(
    conservation_units_tc, 
    inverse = TRUE
  ) %>% 
  # cut indigenous lands
  mask(
    indigenous_lands_tc, 
    inverse = TRUE
  )
```

## Masking raster

```{r}
transport_cost_muni <- extract(
  # extract from raster
  transport_cost_unprotected, 
  municipalities_tc, 
  fun = mean, 
  na.rm = TRUE,
  touches = TRUE,
  bind = TRUE) %>% 
  # return to sf format
  st_as_sf() %>% 
  rename(
    transport_cost = cost_raster_raster_proj
  ) %>% 
  # reverse CRS to standard
  st_transform(
    st_crs(municipalities)
  ) %>% 
  # filter to amazon
  filter(
    code_state %in% amazon_states
  )
```

## Map

```{r}
ggplot() +
  geom_sf(
    data = transport_cost_muni,
    aes(
      geometry = geometry,
      fill = transport_cost
      ),
    color= NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    )
```
## Generate RDS

```{r}
write_rds(
  transport_cost_muni,
  file = "../Variables/transport_cost_muni.rds"
)
```

# Distance to slaughterhouses


