---
title: "Transportation Costs"
author: "Shai Vaz"
date: "May 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(readxl)
library(purrr)

# Graphics
library(ggplot2)

# Geographic
library(sf)
library(terra)

# Personal functions
source("../Functions/bulk_rds.R")
source("../Functions/multi_sum_stats.R")
```

# Importing

## Serialised data

```{r}
bulk_read_rds(
  amc_1991_2022,
  conservation_units,
  indigenous_lands
  )
```

## Transportation Costs

```{r}
tc <- rast(
  x = "../Inputs/cost_raster_raster_proj.tif"
  )
```

## AMC terra vector

```{r}
amc_tr <- amc_1991_2022 |> 
  # remove amc area column
  select(
    - area_amc
  ) |> 
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```

## Conservation Units

There are two groups of Conservation Units. Integral Protection (PI) areas have the objective of preserving nature, with only the indirect use of its natural resources being permitted. Sustainable Use (US) areas have the aim of reconciling nature conservation with sustainable use of natural resources.

```{r}
conservation_units_tr <- conservation_units |>
  # filter only Integral Protection
  filter(
    group == "PI"
  ) |> 
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```

## Indigenous Lands

```{r}
indigenous_lands_tr <- indigenous_lands |>
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```

# Transportation costs per AMC

I use a raster of quality adjusted transportation cost to major ports, developed by Rafael Araujo.

## Removing protected areas

Here I'll remove conservation units and indigenous lands from the cost raster.

```{r}
tc_unprotected <- tc |> 
  # cut conservation units
  mask(
    conservation_units_tr,
    inverse = TRUE
  ) |> 
  # cut indigenous lands
  mask(
    indigenous_lands_tr, 
    inverse = TRUE
  )
```

## TC - Summary statistics by AMC

```{r}
# Perform the extract and manually assign column names
tc_by_amc <- terra::extract(
  tc,
  amc_tr, 
  fun = multi_sum_stats, 
  na.rm = TRUE,
  touches = TRUE,
  bind = TRUE
  ) |> 
  # Return to sf format and reverse CRS
  st_as_sf() |> 
  st_transform(
    st_crs(amc_1991_2022)
    )

# Assign column names manually after extraction
colnames(tc_by_amc) <- c(
  "code_amc", "tc_mean", "tc_median", 
  "tc_q1_mean", "tc_q2_mean", 
  "tc_q3_mean", "tc_q4_mean", 
  "tc_sd", "tc_iqr",
  "geometry"
  )
```

**Check NAs**

## Map

```{r}
ggplot() +
  geom_sf(
    data = tc_by_amc |>  mutate(na = is.na(tc_mean)),
    aes(
      geometry = geometry,
      fill = na
      ),
    color= NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    )
```

## Generate RDS

```{r}
bulk_write_rds()
```

# Distance to slaughterhouses

## Reading

```{r}
sh <- st_read(
  "../Inputs/slaughterhouses/limites_frigorificos_2021.shp",
  quiet = T
  ) |> 
  st_transform(
    crs = st_crs(municipalities)
  )
```

```{r}
sh_active <- sh |> 
  filter(
    situacao == "Ativo"
  )
```

## Plot points

```{r}
ggplot() +
  geom_sf(
    data = municipalities,
    aes(geometry = geom),
    color = "darkgrey",
    fill = NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    ) +
  geom_sf(
    data = sh |> 
      filter() ,
    aes(
      geometry = geometry,
      color = situacao
    )
  )
```

```{r}
sh_distance <-  municipalities |>
  mutate(
    centroid = st_centroid(geom)
  ) |>
  mutate(
    nearest_point_index = st_nearest_feature(centroid, sh_active)
  ) |>
  mutate(
    distance_to_sh = st_distance(
      centroid, 
      sh_active[nearest_point_index, ], 
      by_element = TRUE)
  ) |> 
  mutate(
    distance_to_sh = as.numeric(distance_to_sh)/1000 #change to km
  ) |>
  select(-nearest_point_index) 
```

```{r}
ggplot() +
  geom_sf(
    data = sh_distance |> 
      filter(code_state %in% amazon_states),
    aes(
      geometry = geom,
      fill = distance_to_sh
      ),
    color = NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    )
```

# Market Access

```{r}
market_access <- read_csv(
  file = "../Inputs/Market_access.csv",
  col_types = c("c","c","n", "n","n","l")
  )
```

For now, we'll simply repeat data from 2000's to each municipality, using the AMCs.

```{r}
market_acess_by_muni <- left_join(
  # AMCs in 1991 by municipalities
  amc_1991_by_muni |> 
    as_tibble() |> 
    select(code_amc, muni),
  # Market access by AMC
  market_access |> 
    select(amc, "2000"),
  by = join_by("code_amc" == "amc")
  ) |> 
  mutate(
    market_access_2000 = `2000`/max(`2000`, na.rm = TRUE)*100
  ) |> 
  select(-c("2000"))
```

GET BY NEW AMC
