---
title: "Transportation Costs"
author: "Shai Vaz"
date: "May 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(readxl)
library(purrr)

# Graphics
library(ggplot2)

# Geographic
library(sf)
library(terra)

# Personal functions
source("../Functions/bulk_rds.R")
source("../Functions/multi_sum_stats.R")
```

# Importing

## Serialised data

```{r}
bulk_read_rds(
  amc_1991_2022,
  muni_to_amc
  )
```

## Transportation Costs


I use a raster of quality adjusted transportation cost to major ports, developed by Rafael Araujo. 

```{r}
tc <- rast(
  x = "../Inputs/cost_raster_raster_proj.tif"
  )
```

# Protected areas

This section removes the protected areas. I don't use this version in the main dataframe.

```{r, eval=FALSE}
bulk_read_rds(
  conservation_units,
  indigenous_lands,
  )
```

## Conservation Units

There are two groups of Conservation Units. Integral Protection (PI) areas have the objective of preserving nature, with only the indirect use of its natural resources being permitted. Sustainable Use (US) areas have the aim of reconciling nature conservation with sustainable use of natural resources.

```{r, eval=FALSE}
conservation_units_tr <- conservation_units |>
  # filter only Integral Protection
  filter(
    group == "PI"
  ) |> 
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```

## Indigenous Lands

```{r, eval=FALSE}
indigenous_lands_tr <- indigenous_lands |>
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```

## Removing protected areas

Here I'll remove conservation units and indigenous lands from the cost raster.

```{r, eval=FALSE}
tc_unprotected <- tc |> 
  # cut conservation units
  mask(
    conservation_units_tr,
    inverse = TRUE
  ) |> 
  # cut indigenous lands
  mask(
    indigenous_lands_tr, 
    inverse = TRUE
  )
```

# Transportation costs per AMC

## AMC terra vector

```{r}
amc_tr <- amc_1991_2022 |> 
  # remove amc area column
  select(
    - area_amc
  ) |> 
  # match crs with raster
  st_transform(
    crs(tc)
  ) |>
  # save with terra
  vect()
```


## TC - Summary statistics by AMC

```{r}
# Perform the extract and manually assign column names
tc_by_amc <- terra::extract(
  tc,
  amc_tr, 
  fun = multi_sum_stats, 
  na.rm = TRUE,
  touches = TRUE,
  bind = TRUE
  ) |> 
  # Return to sf format and reverse CRS
  st_as_sf() |> 
  st_transform(
    st_crs(amc_1991_2022)
    )

# Assign column names manually after extraction
colnames(tc_by_amc) <- c(
  "code_amc", "tc_mean", "tc_median", 
  "tc_q1_mean", "tc_q2_mean", 
  "tc_q3_mean", "tc_q4_mean", 
  "tc_sd", "tc_iqr",
  "geometry"
  )

tc_by_amc <- tc_by_amc |> 
  as_tibble() |> 
  select(-geometry)
```

And I remove the original dataframes.

```{r}
rm(
  tc, amc_tr  
)
```

## Check NAs

```{r}
tc_by_amc |>
  filter(
    is.na(tc_mean)
  ) |> 
  as_tibble() |> 
  select(code_amc) |> 
  left_join(
    muni_to_amc,
    
    by = "code_amc"
  ) |> 
  as_tibble() |> 
  select(- geom)
```

## Map

```{r}
tc_by_amc |> 
  left_join(
    amc_1991_2022 |>  select(code_amc, geom),
    by = "code_amc"
  ) |> 
  ggplot() +
    geom_sf(
      aes(
        geometry = geom,
        fill = tc_median
        ),
      color= NA
      ) +
    theme_minimal() +
    theme(
      axis.title=element_blank(),
      axis.text=element_blank(),
      axis.ticks=element_blank()
      )
```

# Distance to slaughterhouses

I'll deal with these data later!

## Reading

```{r, eval=FALSE}
sh <- st_read(
  "../Inputs/slaughterhouses/limites_frigorificos_2021.shp",
  quiet = T
  ) |> 
  st_transform(
    crs = st_crs(municipalities)
  )
```

```{r, eval=FALSE}
sh_active <- sh |> 
  filter(
    situacao == "Ativo"
  )
```

## Plot points

```{r, eval=FALSE}
ggplot() +
  geom_sf(
    data = municipalities,
    aes(geometry = geom),
    color = "darkgrey",
    fill = NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    ) +
  geom_sf(
    data = sh |> 
      filter() ,
    aes(
      geometry = geometry,
      color = situacao
    )
  )
```

```{r, eval=FALSE}
sh_distance <-  municipalities |>
  mutate(
    centroid = st_centroid(geom)
  ) |>
  mutate(
    nearest_point_index = st_nearest_feature(centroid, sh_active)
  ) |>
  mutate(
    distance_to_sh = st_distance(
      centroid, 
      sh_active[nearest_point_index, ], 
      by_element = TRUE)
  ) |> 
  mutate(
    distance_to_sh = as.numeric(distance_to_sh)/1000 #change to km
  ) |>
  select(-nearest_point_index) 
```

```{r, eval=FALSE}
ggplot() +
  geom_sf(
    data = sh_distance |> 
      filter(code_state %in% amazon_states),
    aes(
      geometry = geom,
      fill = distance_to_sh
      ),
    color = NA
    ) +
  theme_minimal() +
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank()
    )
```

# Market Access

## Open data

```{r}
market_access <- read_csv(
  file = "../Inputs/Market_access.csv",
  col_types = c("c","c","n", "n","n","l")
  )
```

## Update AMCs

I need to update this data to the "updated amcs". I'll also take advantage of the federation state information for each AMC in this dataframe. I'll also calculate

```{r}
ma <- market_access |>
  # remove "-" row
  filter(
    ! amc == "-"
  ) |> 
  # Update AMC codes
  mutate(
    code_amc = case_when(
      amc == "2020" ~ "99001",
      amc == "14440" ~ "99002",
      amc == "14413" ~ "99003",
      amc == "15038" ~ "99004",
      # Paraíso das Águas:
      amc == "1085" ~ "99005",
      amc == "1103" ~ "99005",
      amc == "1107" ~ "99005",
      .default = amc
    )
  ) |> 
  # For Paraiso das Aguas, I'll select the maximum for aggregation
  summarise(
    # group by new amc
    .by = code_amc,
    ma_1991 = max(`1991`),
    ma_2000 = max(`2000`),
    ma_2010 = max(`2010`),
    code_state  = unique(Sigla)
  ) |> 
  # calculate normalized market access
  mutate(
    ma_1991_norm = ma_1991/max(ma_1991),
    ma_2000_norm = ma_2000/max(ma_2000),
    ma_2010_norm = ma_2010/max(ma_2010)
  )
```

And I remove the original dataframe.

```{r}
rm(market_access)
```

## Check non-coverage

Compared to my larger AMC dataframe, I have no market access for Fernando de Noronha. This is not a problem, as that municipality is an isolated island and a natural protection zone.

```{r}
  anti_join(
    amc_1991_2022 |> as_tibble() |> select(code_amc),
    a,
    by = "code_amc"
  ) |> 
  left_join(
    muni_to_amc,
    
    by = "code_amc"
  ) |> 
  as_tibble() |> 
  select(- geom)
```

# Generate RDS

```{r}
bulk_write_rds(
  # market access
  ma,
  # transportation costs
  tc_by_amc
)
```
