---
title: "Carbon biomass"
author: "Shai Vaz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(glue)
library(curl)

# Geographic
library(sf)
library(terra)
library(exactextractr)

# Personal functions
source("../Functions/bulk_rds.R")
source("../Functions/process_biomass.R")
```

# Importing external files

```{r}
bulk_read_rds(
  brazil,
  amc_1991_2022
)
```


# Preparing data

This is a very memory-intensive process. The data is divided in large tiles of satellite imagery. In a shape-file, I have data on the tiles location. First, I select data on the tiles in Brazil, and save the links to the API with pixel level data on each tile.

I wrote two functions in order to open each tile, save the raster, and use the exact_extract algorithm to get zonal sum by AMC, by tile. This function is applied each of the 17 tiles in the Brazilian territory. Finally, I aggregated all the 17 zonal statistics by AMC, resulting in the sum of carbon biomass in each zone.

## Open shapefile

First, I open the metadata on the tiles, saved in a shapefile, which contains the location and the API link to download the raster.

```{r}
c_meta <- st_read(
  "../Inputs/carbon_biomass/Aboveground_Live_Woody_Biomass_Density.shp"
  ) 

# Reproject the dataframe
# Use the same CRS as Brazil (SIRGAS 2000) 

c_meta <- st_transform(
  c_meta,
  st_crs(brazil)
  )
```

## Subset region

Then, I intersect with the shape of the Brazilian territory. In sequence, I extract the links to the API with pixel level data on each tile.

```{r}
c_meta_br <- st_intersection(
  c_meta,
  brazil
)

links <- setNames(
  # save links as list
  as.list(c_meta_br$Mg_px_1_do), 
  # take id as names
  c_meta_br$tile_id
  )
```

## Align AMC CRS to raster's

Here, I set the CRS of my AMC polygons to the same of the carbon biomass rasters (WGS 84).

```{r}
amc_84 <- st_transform(
  amc_1991_2022,
  crs = "EPSG:4326"
  ) |> 
  select(-area_amc)
```

# Download and save the rasters

```{r}
download_biomass(
  api_links = links,
  folder_path = "../Biomass"
  )
```



