---
title: "Data Unification"
author: "Shai Vaz"
date: "May 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(readxl)

# Graphics
library(ggplot2)

# Geographic
library(sf)

# Econometrics
library(plm)
library(fixest)
```

# Importing files

```{r}
# cattle_heads_ppm
national_prices
cattle_prices_2017_census
cattle_price_2017_cepea
# municipalities
sh_distance
# transport_cost_muni
# pasture_cover
```

# Intensity per municipality

```{r}
pasture_intensity <- inner_join(
  cattle_heads_ppm,
  
  pasture_cover,
  by = c("code_muni", "year")
  ) %>% 
  mutate(
    intensity = cattle_heads/pasture_cover
  )
```

```{r}
summary(pasture_intensity$intensity)
```

# Local prices panel

## Panel creation

```{r}
panel_1 <- left_join(
  cattle_heads_ppm %>%
    select(year, code_muni, cattle_heads),
  
  municipalities_with_biomes %>% 
    as_tibble() %>% 
    select(-c(11)),
  by = "code_muni"
  ) %>% 
  inner_join(
  cattle_prices_2017_census %>% 
    drop_na(average_price) %>% 
    select(c(1,5)),
  
  by = "code_muni"
  ) %>% 
  mutate(
    year = as.numeric(year),
  ) %>% 
  left_join(
    national_prices,
    by = "year"
  ) %>% 
  mutate(
    local_price = cattle_price*average_price*1000/cattle_price_2017_cepea
  ) %>% 
  filter(
    year >= 2005 
  ) %>% 
  left_join(
    market_acess_by_muni %>% 
      select(-code_amc),
    by = c("code_muni" = "muni")
  ) %>%
  left_join(
    sh_distance %>%
      as_tibble() %>% 
      select(code_muni, distance_to_sh),
    by = "code_muni"
  ) %>% 
  mutate(
    iceberg_cost = 1/distance_to_sh
  ) %>% 
  unique() %>% 
  filter(
    amazonia == TRUE
  )
```

```{r}
panel_2 <- 
  inner_join(
  cattle_prices_2017_census %>% 
    drop_na(average_price),
  
  pasture_intensity %>% 
    drop_na(intensity) %>% 
    select(
      year, 
      code_muni, 
      muni_state, 
      cattle_heads, 
      pasture_cover, 
      intensity
    ),
  by = "code_muni"
  ) %>% 
  mutate(
    year = as.numeric(year),
    muni_state = as.factor(muni_state),
    name_state = as.factor(name_state)
  ) %>% 
  left_join(
    national_prices,
    by = "year"
  ) %>% 
  mutate(
    local_price = cattle_price*average_price*1000/cattle_price_2017_cepea,
    chicken_price = chicken_price*1000 #in ton
  ) %>% 
  select(
    year, 
    code_muni, 
    muni_state,
    name_state,
    cattle_heads, 
    pasture_cover, 
    intensity,
    local_price,
    chicken_price
  ) %>% 
  filter(
    year >= 2005
  ) %>% 
  left_join(
    sh_distance %>%
      as_tibble() %>% 
      select(code_muni, distance_to_sh),
    by = "code_muni"
  ) %>% 
  mutate(
    iceberg_cost = 1/distance_to_sh
  ) 
```

## Panel Linear Model

```{r}
y <- pdata.frame(
  panel_1, 
  index= c("code_muni","year"),
  drop.index = FALSE, 
  row.names = TRUE) %>% 
  mutate(
    shifter = plm::lag(chicken_price)*market_access_2000
  )
```

# Regressions

## First stage

```{r}
s1 <- plm(
  local_price ~ shifter,
  data = y,
  model = "within",
  effect = "individual"
  )

summary(s1)
```

## Second Stage

### Baseline

```{r}
model_1 <- plm(
  cattle_heads ~ local_price + lag(local_price) | . - local_price + shifter,
  data = y,
  model = "within",
  effect = "individual"
  )

summary(model_1)
```

```{r}
delta = 1/as.vector(model_1$coefficients)[2]*1/0.9
phi1 = - delta * as.vector(model_1$coefficients)[1]

print(phi1)
```

### Controlling for pasture area

```{r}
model_2 <- plm(
  cattle_heads ~ local_price + lag(local_price) + pasture_cover | . - local_price - pasture_cover + lag(chicken_price,1:2):iceberg_cost + lag(pasture_cover),
  data = y,
  model = "within",
  effect = "individual"
  )

summary(model_2)
```

```{r}
delta = 1/as.vector(model_2$coefficients)[2]*1/0.9
phi1 = - delta * as.vector(model_2$coefficients)[1]

print(phi1)
```

### Baseline in logs

```{r}
model_3 <- plm(
  log(cattle_heads) ~ local_price + lag(local_price) | . - local_price + shifter,
  data = y,
  model = "within",
  effect = "individual"
  )

summary(model_3)
```

```{r}
delta = 1/as.vector(model_3$coefficients)[2]*1/0.9
phi1_log = - delta * as.vector(model_3$coefficients)[1]

print(phi1_log)
```

### Log and time trend

```{r}
model_4 <- plm(
  log(cattle_heads) ~ local_price + lag(local_price) + as.numeric(year) | . - local_price + shifter,
  data = y,
  model = "within",
  effect = "individual"
  )

summary(model_4)
```

```{r}
delta = 1/as.vector(model_4$coefficients)[2]*1/0.9
phi1 = - delta * as.vector(model_4$coefficients)[1]

print(phi1)
```

### Level and time trend

```{r}
model_5 <- plm(
  cattle_heads ~ local_price + lag(local_price) + as.numeric(year) | . - local_price + shifter,
  data = y,
  model = "within",
  effect = "individual"
  )

summary(model_5)
```

```{r}
delta = 1/as.vector(model_5$coefficients)[2]*1/0.9
phi1 = - delta * as.vector(model_5$coefficients)[1]

print(phi1)
```

# Testing Outliers

```{r}
a <- panel_1 %>%
  group_by(code_muni) %>% 
  mutate(
    lag_cattle_heads = dplyr::lag(cattle_heads),
    cattle_heads = cattle_heads,
    lead_cattle_heads = dplyr::lead(cattle_heads),
    
    lag_var_heads = cattle_heads/dplyr::lag(cattle_heads)-1,
    
    lead_var_heads = dplyr::lead(cattle_heads)/cattle_heads-1,

    z_score = (cattle_heads - mean(cattle_heads, na.rm = TRUE))/sd(cattle_heads)
  ) %>% 
  filter(
    year > 2005
  )
```

```{r}
quantile(a$z_score, c(0.0001, 0.0005, 0.001, 0.999, 0.9995, 0.9999), na.rm=TRUE)
```

```{r}
b <- a %>% 
  filter(
     z_score < -2.898154 
     | z_score > 3.118212
  )
```

```{r}
P = ecdf(a$z_score)
(1-P(3.4))*100 + P(-3.2)*100 - 1
```

### New Panel

```{r}
c <- a %>% 
  ungroup() %>% 
  filter(
     z_score > -2.473873  
     & z_score < 2.999128
  ) 
```

```{r}
d <- pdata.frame(
  c, 
  index= c("code_muni","year"),
  drop.index = FALSE, 
  row.names = TRUE) %>% 
  mutate(
    shifter = plm::lag(chicken_price)*market_access_2000
  )
```

## Regressions

## First stage

```{r}
s1_d <- plm(
  local_price ~ shifter,
  data = d,
  model = "within",
  effect = "individual"
  )

summary(s1_d)
```

## Second Stage

### Baseline

```{r}
model_d <- plm(
  cattle_heads ~ local_price + lag(local_price) | . - local_price + shifter,
  data = d,
  model = "within",
  effect = "individual"
  )

summary(model_d)
```

# Stargazer

```{r}
library(stargazer)
```

First stage

```{r}
stargazer(
  s1,
  title = "First Stage Regression",
  header = FALSE,
  dep.var.labels = "Local Price",
  covariate.labels = "Suppply Shifter Instrument"
  )
```

And second stage:

```{r}
stargazer(
  model_1,
  title = "Second Stage Regression",
  header = FALSE,
  dep.var.labels = "Cattle heads",
  covariate.labels = c("Local Price", "Lagged Local Price"),
   add.lines= list(c("(1+Phi)", round(phi1,digits = 3))),
  label = "second_stage"
  )
```

Log baseline.

```{r}
stargazer(
  model_3,
  title = "Second Stage Regression",
  header = FALSE,
  dep.var.labels = "Log Cattle heads",
  covariate.labels = c("Local Price", "Lagged Local Price"),
   add.lines= list(c("(1+Phi)", round(phi1_log,digits = 3))),
  label = "log_reg"
  )
```

With other shifter (BRL):
