---
title: "Data Unification"
author: "Shai Vaz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(knitr.kable.NA = '')
```

```{r, include=FALSE}
# Table
library(kableExtra)
library(tinytable)

# Graphics
library(ggplot2)
library(ggpattern)

# Geographic
library(sf)

# Econometrics
library(fixest)
library(ivreg)
library(stats)
library(modelsummary)

# Data Wrangling
library(dplyr)
library(readr)
library(tidyr)
library(stringr)
library(readxl)
library(forcats)
library(purrr)

# Personal functions
source("../Functions/bulk_rds.R")
```

# Importing files

```{r}
bulk_read_rds(
  # geographic
  muni_to_amc,
  amc_1991_2022,
  brazil,
  # prices
  national_prices,
  cattle_prices_cepea_in_census_years,
  ipca_census_years,
  # census data
  agg_census_data,
  # survey data
  cattle_heads_ppm,
  # instruments
  ssiv,
  # controls
  tc_by_amc,
  ma_long,
  si_by_amc,
  # mapbiomas
  land_cover_agg,
  transition_agg,
  past_qual,
  # carbon biomass
  biomass
  )
```

Read terraclimate climatic controls. 

```{r}
terraclimate <- read_csv(
  "../Variables/terraclimate.csv", 
  col_types = "cnnnnnnnn")
```

# Joining database

```{r}
int_data <- left_join(
  # first I join shifters with prices
  # then I extract data from t+1
  ssiv |> 
    select(code_amc, year, area_amc, ssiv),
  
  cattle_prices_cepea_in_census_years,
  
  by = c("year" = "census_year")
  ) |> 
  ########## get next period prices and shifters
  mutate(
    mean_price_2 = if_else(
      year == 2006 | year == 2017,
      lead(mean_price),
      NA),
    
    mean_nominal_price_2 = if_else(
      year == 2006 | year == 2017,
      lead(mean_nominal_price),
      NA),
    
    ssiv_2 = if_else(
      year == 2006 | year == 2017,
      lead(ssiv),
      NA)
  ) |>
  ############ join with census data
  right_join(
    agg_census_data,
    
    by = c("code_amc", "year")
  ) |>
    # drop observations without cattle sales
  filter(
    ! is.na(av_price_slaughter)
  ) |> 
    # calculate normalized head count (intensity)
  mutate(
    h = cattle_heads_big/area_amc
  ) |> 
  ############ join with inflation
  left_join(
    ipca_census_years,
    
    by = c("year" = "census_year")
  ) |> 
  ############ deflate and project ahead local prices
             # using IPCA ratio (index_2022/index)
  mutate(
    local_price = av_price_slaughter * (index_2022/index)
                  *1000,
    
    local_price_2 = av_price_slaughter *(index_2022/index)
                    *(mean_price_2/mean_price)*1000,
  ) |> 
  ############# include controls
  left_join(
    tc_by_amc,
    by = "code_amc"
  ) |> 
  left_join(
    ma_long,
    by = c("code_amc", "year")
  ) |> 
  left_join(
    si_by_amc,
    by = "code_amc"
  ) |> 
  ############ include land use
  left_join(
    land_cover_agg,
    
    by = c("code_amc", "year")
  ) |> 
              # calculate pasture share (in t and only in 2006)
  mutate(
    past_share = if_else(is.na(pasture), 0, pasture/area_amc),
    
    pasture_2006 = if_else(year == 2006, pasture, lag(pasture)),
    
    past_share_2006 = if_else(is.na(pasture_2006), 0, pasture_2006/area_amc)
  ) |> 
  ############ include pasture quality
  left_join(
    past_qual |> 
            ####### testing lead high share
            mutate( 
              .by = code_amc,
              high_share = dplyr::lead(high_share)
            ),
    by = c("code_amc", "year")
  ) |>
            # filter out one NA on total pastures
            # only case is Afuá-PA (in Marajó island)
  filter(
    ! is.na(total)
  ) |> 
  ########### include carbon biomass
  left_join(
    biomass,
    by = "code_amc"
  ) |> 
            # calculate carbon density in CO2
            # uses atomic weight of C (12) and CO2 (44)
            # and the fact that biomass is about 50% C
  mutate(
    biomass_co2 = (biomass/2)*(44/12),
    biomass_density = biomass_co2/area_amc
  ) |> 
  ############ terraclimate controls
  left_join(
    terraclimate,
    
    by = c("code_amc", "year")
  )
```

# Intensive margin

## IV 

```{r}
iv <- feols(
  data = int_data,
  h ~
    ma_norm
  + si_median
  + year
  + tmmn_min + tmmx_max
  + tmmn_mean + tmmx_mean

  | sw(1,main_biome, code_state)
  
  | local_price + local_price_2 + high_share ~ ssiv + ssiv_2 + pr,
  
  panel.id = c("code_amc","year"),
  cluster = "code_amc"
  )

etable(
  iv, 
  stage=2, 
  digits = 4,
  fitstat = ~ n + f + ivf)
```

Etable with phi:

```{r}
phi_iv = function(x) {
  # Extract coefficients
  coefs <- stats::coef(x)
  
  # Calculate phi
  phi <- - coefs["fit_local_price_2"] / (beta * coefs["fit_local_price"]) - 1
  
  # Return phi value
  return(phi)
}

extralines_register("phi_iv", phi_iv, "phi")


etable(
  iv, 
  stage = 2, 
  digits = 4,
  fitstat = ~ n + f + ivf,
  extralines = ~ phi_iv
)

```


## OLS 

```{r}
ols <- feols(
  data = int_data,
  h ~
    local_price
  + local_price_2
  + high_share
  + ma_norm
  + si_median
  + year
  + tmmn_min
  + tmmx_max 
  + tmmn_mean
  + tmmx_mean
  
  + high_share
  
  | sw(1,main_biome,code_state, code_amc),
  panel.id = c("code_amc","year"),
  cluster = "code_amc"
  )

etable(
  ols, 
  stage=2, 
  digits = 5,
  fitstat = ~ n + f + ivf
  )
```


```{r}
phi_ols = function(x) {
  # Extract coefficients
  coefs <- stats::coef(x)
  
  # Calculate phi
  phi <- ( - coefs["local_price_2"] ) / (beta * coefs["local_price"]) - 1
  
  # Return phi value
  return(phi)
}

extralines_register("phi_ols", phi_ols, "phi")

etable(
  ols, 
  stage = 2, 
  digits = 4,
  fitstat = ~ n + f + wf + r2 + wr2 + ar2,
  extralines = ~ phi_ols
)

```

# Diagnostics (one iv)

```{r, eval=FALSE}
a <- joined_data |> 
  mutate(
    fe = as_factor(code_amc),
    fe_2 = as_factor(main_biome)
  ) |> 
  drop_na() |> 
  filter(
    cattle_heads_big != 0
  )
```

```{r, eval=FALSE}
first_stage1 <- lm(local_price ~ ssiv, data = a)
first_stage2 <- lm(local_price_2 ~ ssiv_2, data = a)

# Extract predicted values
a$local_price_hat <- predict(first_stage1)
a$local_price_2_hat <- predict(first_stage2)
```

```{r, eval=FALSE}
iv_model <- ivreg(
  cattle_heads_big ~ local_price_hat + local_price_2_hat:fe_2 + fe_2, 
  data = a
)


summary(iv_model)
```

# Extensive margin

Import Euler-Mascheroni constant:

```{r}
gamma = -digamma(1)
```

I'll also define the discount parameter, beta.

```{r}
beta = 0.9
```

Create a function to calculate the intertemporal difference $\beta x_{mt+1} - x_{mt}$:

```{r}
tdif = \(x) beta * dplyr::lead({{x}}) - {{x}} 
```


```{r}
ext_data <- transition_agg |> 
  ############# get transition probabilities
  select(
    code_amc,
    year = year_to,
    rho_1 = natural_pasture
  ) |> 
  mutate(
    rho_2 = lead(rho_1),
    .by = code_amc
  ) |> 
  ########### include ssiv
  left_join(
    ssiv |>  select(code_amc, area_amc, ssiv, year),
    
    by = c("code_amc", "year")
  ) |> 
  ############ join with census data
  left_join(
    agg_census_data |> 
      select(
        year,
        code_amc, 
        main_biome,
        cattle_heads,
        cattle_heads_big
      ),
    
    by = c("code_amc", "year")
  ) |> 
  # calculate normalized head count (intensity)
  mutate(
    h = cattle_heads_big/area_amc
  ) |>
  ############# include controls
  left_join(
    tc_by_amc |> select(code_amc, tc_mean, tc_median),
    by = "code_amc"
  ) |> 
  left_join(
    ma_long,
    by = c("code_amc", "year")
  ) |> 
  left_join(
    si_by_amc |> select(code_amc, si_mean, si_median),
    by = "code_amc"
  ) |>
  ############ include land use
  left_join(
    land_cover_agg,
    
    by = c("code_amc", "year")
  )  |> 
  ############ include pasture quality
  left_join(
    past_qual,
    by = c("code_amc", "year")
  ) |> 
  ############ terraclimate controls
  left_join(
    terraclimate,
    
    by = c("code_amc", "year")
  )|> 
  ########### include carbon biomass
  left_join(
    biomass,
    by = "code_amc"
  ) |> 
  # calculate carbon density in CO2
  mutate(
    biomass_co2 = (biomass/2)*(44/12),
    biomass_density = biomass_co2/area_amc
  ) |> 
  ############# calculate regression variables
  # difference in cost factors
  mutate(
    .by = "code_amc",
    across(
      .cols = c(high_share, tmmn_min:tmmx_mean, pr),
      .fns = tdif,
      .names = "{.col}_tdif"
      )
  ) |> 
  mutate(
    .by = "code_amc",
    
    pr_lag = dplyr::lag(pr),
    
    y = log(rho_1/(1-rho_1)) - beta* log(rho_2) + beta*gamma,
    
    x1 = 0.45*(cattle_heads_big**2),
    
    x2 = 0.45*(h)**2,
    
    x3 = 0.45*(cattle_heads_big/pasture)**2,
    
    x4 = 0.45*(cattle_heads/area_amc)**2,
    
    x5 = 0.45*(cattle_heads/pasture)**2,
    
    year_tdif = (beta + (beta - 1) * year)
  ) |> 
  ############# remove probability 0 and 1 (impossible log odds)
  filter(
    rho_1 != 0 &
    rho_1 != 1 &
    rho_2 != 0 
  ) |> 
  ############ filter to census years
  filter(
    year == 2006 | year == 2017
  ) |> 
  ########## remove NA
  filter(
    !is.na(x2)
  )
```


## IV with Census

```{r}
ext_iv <- feols(
  data = ext_data,
  y ~ 
  x2
#  + high_share_tdif
  + ma_norm
  + si_median
  + biomass_density
  + year_tdif
  + tmmn_min_tdif + tmmx_max_tdif 
  + tmmn_mean_tdif + tmmx_mean_tdif
  + pr_tdif
    
  | sw(1,main_biome, code_state)
  | high_share_tdif ~ pr,

  cluster = "code_amc"
  )

etable(
  ext_iv,
  fitstat = ~ n + f + ivf
  )
```

## OLS with census

```{r}
ext_ols <- feols(
  data = ext_data,
  y ~ 
  x2
  + high_share_tdif
  + ma_norm
  + si_median
  + biomass_density
  + year_tdif
  + tmmn_min_tdif + tmmx_max_tdif 
  + tmmn_mean_tdif + tmmx_mean_tdif
  + pr_tdif
    
  | sw(1,main_biome, code_state),
  cluster = "code_amc"
  )

etable(
  ext_ols,
  fitstat = ~ n + f + ivf
  )
```

# PPM version

```{r}
ch_ppm_amc <- cattle_heads_ppm |> 
  ########### get PPM data
  left_join(
    muni_to_amc |> select(-name_muni),
    by = join_by(code_muni)
  ) |> 
  ########### aggregate by AMC
  summarise(
    .by = c("code_amc", "year"),
    
    cattle_heads = sum(cattle_heads, na.rm = TRUE),
    main_biome = unique(main_biome)
  ) |> 
  mutate(
    year = as.numeric(year)
  )
```

```{r}
ext_ppm <- transition_agg |> 
  ############# get transition probabilities
  select(
    code_amc,
    year = year_to,
    rho_1 = natural_pasture
  ) |> 
  mutate(
    rho_2 = lead(rho_1),
    .by = code_amc
  ) |> 
  ########### include ssiv
  left_join(
    ssiv |>  select(code_amc, area_amc, ssiv, year),
    
    by = c("code_amc", "year")
  ) |> 
  ############ join with PPM data
  left_join(
    ch_ppm_amc,
    
    by = c("code_amc", "year")
  ) |> 
  # calculate normalized head count (intensity)
  mutate(
    h = cattle_heads/area_amc
  ) |>
  ############# include controls
  left_join(
    tc_by_amc |> select(code_amc, tc_mean, tc_median),
    by = "code_amc"
  ) |>  
  left_join(
    si_by_amc |> select(code_amc, si_mean, si_median),
    by = "code_amc"
  ) |>
  # join with market access for 2010
  left_join(
    ma_long |> 
      filter(year_ma == 2010) |> 
      select(-year_ma, -year),
    
    by = "code_amc"
  ) |>
  ############ include land use
  left_join(
    land_cover_agg,
    
    by = c("code_amc", "year")
  )  |> 
  ############ include pasture quality
  left_join(
    past_qual,
    by = c("code_amc", "year")
  ) |> 
  ############ terraclimate controls
  left_join(
    terraclimate,
    
    by = c("code_amc", "year")
  )|> 
  ########### include carbon biomass
  left_join(
    biomass,
    by = "code_amc"
  ) |> 
  # calculate carbon density in CO2
  mutate(
    biomass_co2 = (biomass/2)*(44/12),
    biomass_density = biomass_co2/area_amc
  ) |> 
  ############# calculate regression variables
  # difference in cost factors
  mutate(
    .by = "code_amc",
    across(
      .cols = c(high_share, tmmn_min:tmmx_mean, pr),
      .fns = tdif,
      .names = "{.col}_tdif"
      )
  ) |> 
  mutate(
    .by = "code_amc",
    
    pr_lag = dplyr::lag(pr),
    
    y = log(rho_1/(1-rho_1)) - beta* log(rho_2) + beta*gamma,
    
    x2 = 0.45*(cattle_heads/area_amc)**2,
    
    x5 = 0.45*(cattle_heads/pasture)**2,
    
    year_tdif = (beta + (beta - 1) * year)
  ) |> 
  ############# remove probability 0 and 1 (impossible log odds)
  filter(
    rho_1 != 0 &
    rho_1 != 1 &
    rho_2 != 0 
  )
```


## OLS with PPM

```{r}
ppm_ols <- feols(
  data = ext_ppm,
  y ~ x2
  + high_share_tdif
  + ma_norm
  + year_tdif
  + biomass_density
  + tmmn_min_tdif + tmmx_max_tdif 
  + tmmn_mean_tdif + tmmx_mean_tdif 
  + pr_tdif
  
  | sw(1, main_biome, code_state),
  cluster = "code_amc"
  )


etable(
  ppm_ols,
  fitstat = ~ n + f + wf + r2)
```

## IV with PPM

```{r}
ppm_iv <- feols(
  data = ext_ppm,
  y ~ x2
  + ma_norm
  + biomass_density
  + year_tdif
  + tmmn_min_tdif + tmmx_max_tdif 
  + tmmn_mean_tdif + tmmx_mean_tdif
#  + pr_tdif
 
  | sw(1, main_biome, code_state)
  | high_share_tdif ~ pr,
  cluster = "code_amc"
  )

etable(
  ppm_iv, 
  stage = 2,
  fitstat = ~ n + f + f.p + ivf + ivf.p)
```

# Counterfactuals

To calculate a counterfactual, I'll choose a pair of models of each margin. Then, I predict the int margin model with real data, and compare the prediction to when a I make a variation in the data.

I calculate the ext margin model for the predicted headcount and for the counterfactual. Probability for the following year remains the same because it is forward looking.

## Selected models

```{r}
######### Int margin - IV model with Biome FE
int_mod <- iv[[2]]

######### Ext margin - OLS model with Biome FE
ext_mod <- ext_iv[[1]]
```


## Main scenarios

```{r}
###############################
########## Intensive margin ###
###############################

# increase pasture quality to at least some%
min_high_share = 0.95

int_cf_data_recovery <- int_data |> 
  mutate(
    high_share = if_else(
      high_share > min_high_share, 
      high_share, 
      min_high_share),
  )

# join counterfactuals with dataframe 
int_cf <- int_data |> 
  mutate(
    h_hat = predict(int_mod),
    h_recovery = predict(int_mod, newdata = int_cf_data_recovery)
  )

################################
######### Extensive margin #####
################################

# Estimated
ext_cf_data_hat <- ext_data |> 
  left_join(
    int_cf |> select(code_amc, year, h_hat, h_recovery),
    
    by = c("code_amc", "year")
  ) |> 
  mutate(
    x2 = 0.45*(h_hat)**2
  )

# Pasture recovery
ext_cf_data_recovery <- ext_cf_data_hat |> 
  mutate(
    # square density
    x2 = 0.45*(h_recovery)**2,
    
    # increase share of high quality
    high_share = if_else(
      high_share > min_high_share, 
      high_share, 
      min_high_share),
  )

# Maximum potential from pasture recovery
# ignoring the effect of increasing productivity
# to separate the two opposing effects
ext_cf_data_potential <- ext_cf_data_hat |> 
  mutate(
    # increase share of high quality
    high_share = if_else(
      high_share > min_high_share, 
      high_share, 
      min_high_share),
  )

# join counterfactuals with dataframe
ext_cf <- ext_data |> 
  mutate(
    # predicted
    y_hat = predict(ext_mod, newdata = ext_cf_data_hat),
    # pasture recovery
    y_recovery = predict(ext_mod, newdata = ext_cf_data_recovery),
    # maximum potential
    y_potential = predict(ext_mod, newdata = ext_cf_data_potential)
    
  )

##########################################
########## calculate new probabilities ###
##########################################

logit = \(x) exp(x)/(1+exp(x))

#ext_cf_final <- 
  
ext_cf |> 
  mutate(
    rho_hat = logit(
      y_hat + beta*log(rho_2) - beta*gamma
      ),
    
    rho_recovery = logit(
      y_recovery + beta*log(rho_2) - beta*gamma
      ),
    
    rho_potential = logit(
      y_potential + beta*log(rho_2) - beta*gamma
      )
  ) |> 
  summarise(
    real = sum(rho_1*natural),
    expected = sum(rho_hat*natural),
    recovery = sum(rho_recovery*natural),
    potential = sum(rho_potential*natural)
  )

```

## Carbon tax

```{r}
counterfactual_prediction <- function(model, new_alpha_b) {
  # Extract original coefficients
  coefs <- coef(model)
  
  # Replace the coefficient of biomass_density with new_alpha_b
  coefs["biomass_density"] <- new_alpha_b
  
  # Extract the design matrix for the predictors used in the model
  design_matrix <- fixest::model.matrix(model)
  
  # Calculate the new predictions (excluding fixed effects)
  y_biomass <- as.vector(design_matrix %*% coefs)
  
  # Add the fixed effects back to the predictions
  fixed_effects <- fixef(model)$main_biome
  fe_mapping <- attr(fixef(model), "fixef_vars")$main_biome
  y_biomass <- y_biomass + fixed_effects[fe_mapping]
  
  # Return the predictions
  return(y_biomass)
}

```

Testing:

```{r}
alpha_b <- coef(ext_mod)["biomass_density"]
new_alpha_b <- -0.10

ext_data |> 
  mutate(
    y_biomass = counterfactual_prediction(ext_mod, alpha_b)
  ) |> 
  select(
    code_amc, year, main_biome, y, y_biomass
  ) |> 
  View()


fixef(ext_mod)$main_biome

model.matrix(ext_mod, type = "fixef") |> head()
```




# Maps

```{r}
map_data <- amc_1991_2022 |> 
  select(-area_amc) |> 
  cross_join(
    tribble(~year, 2006, 2017)
  ) |> 
  right_join(
    ext_data,
    by = c("code_amc", "year")
  )
```

## Prices

```{r}
map_prices <- ggplot() +
  # Plot non-NA local_price values
  geom_sf(
    data = map_data,
    aes(fill = local_price),  # Automatically detects geometry from sf object
    color = NA
  ) +
  # Add outline
  geom_sf(
    data = brazil, 
    color = "lightgrey",
    fill = NA
  ) +
  # Create facets for different years
  facet_wrap(~ year, ncol = 2) +  
  # Apply the color scale
  scale_fill_viridis_c(
    option = "magma",
    direction = -1
  ) + 
  # Adjust themes for cleaner appearance
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = NA, color = NA),
    legend.key.width = unit(0.2, "cm"),
    legend.title = element_blank()
  ) +
  labs(
    title = "Local Prices by Year in Sample",
    subtitle = "Prices per cattle head in R$ of 2022"
  )


#ggsave("../Outputs/Graphics/map_prices.pdf", plot = map_prices, device = "pdf", width = 10, height = 6)
```


## Transitions

```{r}
map_transitions <- ggplot(map_data) +
  geom_sf(
    data = map_data,
    aes(fill = rho_1, geometry = geom), 
    color = NA
    ) +
  facet_wrap(~ year, ncol = 2) +  
  scale_fill_viridis_c(
    option = "rocket",
    direction = -1
    ) +
  geom_sf(
    data = brazil, 
    color = "lightgrey",
    fill = NA
    ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = NA, color = NA),
    legend.key.width = unit(0.2, "cm"),
    legend.title = element_blank()
    ) +
  labs(
    title = "Transition probabilities",
    subtitle = "Yearly conversion rate from natural vegetation to pasture"
    )

map_transitions
#ggsave("../Outputs/Graphics/map_transitions.pdf", plot = map_transitions, device = "pdf", width = 10, height = 6)
```

## Pasture quality

```{r}
map_quality <- ggplot(map_data) +
  geom_sf(
    aes(fill = low_share), 
    color = NA
    ) +
  facet_wrap(~ year, ncol = 2) +  
  scale_fill_viridis_c(
    option = "rocket",
    direction = -1
    ) +
  geom_sf(
    data = brazil, 
    color = "lightgrey",
    fill = NA
    ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = NA, color = NA),
    legend.key.width = unit(0.2, "cm"),
    legend.title = element_blank()
    ) +
  labs(
    title = "Pasture quality",
    subtitle = "Share of pastures with low vegetative vigour by year"
    )

map_quality
#ggsave("../Outputs/Graphics/map_quality.pdf", plot = map_quality, device = "pdf", width = 10, height = 6)
```

## Biomass density

```{r}
map_biomass <- map_data |> 
  filter(year == 2017) |>
  ggplot() +
  geom_sf(
    aes(fill = biomass_density), 
    color = NA
    ) +  
  scale_fill_viridis_c(
    direction = -1
    ) +
  geom_sf(
    data = brazil, 
    color = "lightgrey",
    fill = NA
    ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = NA, color = NA),
    legend.key.width = unit(0.2, "cm"),
    legend.title = element_blank()
    ) +
  labs(
    title = "Aboveground Biomass",
    subtitle = "Density of AGB in CO2-equivalent tons per hectare"
    )

ggsave("../Outputs/Graphics/map_biomass.pdf", plot = map_biomass, device = "pdf", width = 8, height = 8)
```


# Plots

## Cattle heads

```{r}
plot_ch <- ext_ppm |> 
  summarise(
    ch = sum(cattle_heads),
    .by = c(code_biome, main_biome, year)
  ) |> 
  mutate(
    Bioma = case_when(
      code_biome == 1 ~ "Amazônia",
      code_biome == 2 ~ "Caatinga",
      code_biome == 3 ~ "Cerrado",
      code_biome == 4 ~ "Mata Atlântica",
      code_biome == 5 ~ "Pampa",
      code_biome == 6 ~ "Pantanal")
  ) |> 
  ggplot() +
  # Line plot with color by biome
  geom_line(
    aes(x = year, y = ch, color = Bioma),
    size = 1
  ) +
  scale_color_manual(
    values = c(
      "Amazônia" = "#1b9e77", 
      "Caatinga" = "#ffbb78",
      "Cerrado" = "#d95f02",
      "Mata Antlântica" = "#66b3ff",
      "Pampa" = "#d62728",
      "Pantanal" = "#9467bd"
      ),
    name = "Main Biome"
  ) +
  # Labels and titles
  labs(
    title = "Cattle Heads Over Time by Main Biome",
    subtitle = "Regional distribution of cattle heads from 2000 to 2022",
    x = "Year",
    y = "Cattle Heads"
  ) +
  # Improved theme
  theme_minimal() +
  theme(
    axis.text = element_text(color = "black")
  )

plot_ch
#ggsave("../Outputs/Graphics/plot_ch.pdf", plot = plot_ch, device = "pdf", width = 10, height = 6)
```

## Pastures

```{r}
land_cover_agg |> 
  left_join(
    select(agg_census_data, c(code_amc, code_biome, main_biome)),
    by = "code_amc"
  ) |> 
  summarise(
    pasture = sum(pasture, na.rm = T),
    .by = c(code_biome, main_biome, year)
  ) |> 
  mutate(
    Bioma = case_when(
      code_biome == 1 ~ "Amazônia",
      code_biome == 2 ~ "Caatinga",
      code_biome == 3 ~ "Cerrado",
      code_biome == 4 ~ "Mata Atlântica",
      code_biome == 5 ~ "Pampa",
      code_biome == 6 ~ "Pantanal")
  ) |> 
  ggplot() +
  # Line plot with color by biome
  geom_line(
    aes(x = year, y = pasture, color = Bioma),
    size = 1
  ) +
  scale_color_manual(
    values = c(
      "Amazônia" = "#1b9e77", 
      "Caatinga" = "#ffbb78",
      "Cerrado" = "#d95f02",
      "Mata Antlântica" = "#66b3ff",
      "Pampa" = "#d62728",
      "Pantanal" = "#9467bd"
      ),
    name = "Main Biome"
  ) +
  # Labels and titles
  labs(
    title = "Pasture area Over Time by Main Biome",
    subtitle = "Regional distribution of pastures from 2001 to 2020",
    x = "Year",
    y = "Pasture area (ha)"
  ) +
  # Improved theme
  theme_minimal() +
  theme(
    axis.text = element_text(color = "black")
  )
```

# Notes

Exchange
2019	3.9445
2022	5.1642

IPCA
2019    5320.25
2022    6474.09

SCC (2019 US$)
66.00

Annuity/perpetuity equivalent
6.60 (2019 US$)
26.0337 (2019 R$)
31.67981 (2022 R$)

Alpha_p
0.0033579724

Result:
-0.1063799


# Regression tables

## Intensive margin

```{r}
get_f_stats <- function(model) {
  map(
    list(
      `F (2nd stage)` = fixest::fitstat(model, "f")$f$stat,
      `F (1st stage: local_price)` = fixest::fitstat(model, "ivf")$`ivf1::local_price`$stat,
      `F (1st stage: local_price_2)` = fixest::fitstat(model, "ivf")$`ivf1::local_price_2`$stat,
      `F (1st stage: high_share)` = fixest::fitstat(model, "ivf")$`ivf1::high_share`$stat),
    
    \(x) round(x, 4)
  )
}

# Rename coefficients
coef_rename <- c(
  "fit_local_price" = "$p_{mt}$",
  "fit_local_price_2" = "$p_{mt+1}$",
  "fit_high_share" = "Pasture Quality ($x_{mt+1}$)",
  "year" = "Year"
)

# Add model parameters as an extra column
model_parameters <- data.frame(
  "Parameters" = c(
  "$-\\dfrac{\\alpha_p}{\\delta \\beta}$", "",
  "$\\dfrac{\\alpha_p (1 + \\phi)}{\\delta}$", "",
  "$-\\dfrac{\\gamma_{pasture}}{\\delta}$", "",
  "$-\\dfrac{\\gamma_t}{\\delta}$")
)

# Add controls, fixed effects, and F-statistics as extra rows
extra_rows <- data.frame(
  rowname = c("Controls", 
              "Fixed Effects", 
              "F (2nd stage)", 
              "F (1st stage: $p_{mt}$)", 
              "F (1st stage: $p_{mt+1}$)", 
              "F (1st stage: Past. Qual.)", 
              "Clustered SE"),
  value = c(
    "Temp.; Past.Suit.; Mkt.Acc.", 
    "Biome", 
    get_f_stats(int_mod)[["F (2nd stage)"]], 
    get_f_stats(int_mod)[["F (1st stage: local_price)"]], 
    get_f_stats(int_mod)[["F (1st stage: local_price_2)"]], 
    get_f_stats(int_mod)[["F (1st stage: high_share)"]], 
    "Yes (Municipality)"),
  mod_par = ""
  )

# Name a model list dynamically 
header = paste0("\\hline", 
                "$h_{mt+1}$")

model_list = setNames(list(int_mod), header)


# Create the table
modelsummary(
  model_list,
  coef_map = coef_rename,
  gof_map = "nobs",
  fmt = 4, 
  statistic = "{std.error}", 
  stars = c("***"=0.01, "**"=0.05, "*"=0.10), 
  add_rows = extra_rows,
  title = "Intensive Margin IV Regression Results\\label{tab:main_int}",
  notes = paste(
    "Standard errors clustered at the municipality level.",
    "Biome fixed effects.",
    "Controls: Pasture suitability, market access, 
      minimum, maximum, and mean temperature.",
    "Shift-share variables used as instruments for prices.",
    "Lagged precipitation used as instruments for pasture quality."
  ),
  add_columns = model_parameters,
  output = "tinytable",
  escape = FALSE,
  width = 1
  ) |>
  style_tt(
    tabularray_inner = "
      row{1} = {valign = m},
      row{2,4,6,8} = {abovesep = 5pt, belowsep = -7pt},
      column{3} = {valign = b}
      "
    ) |> 
  save_tt(
    output = "../Outputs/Tables/main_int_table.tex",
    overwrite = T
  )

remove(get_f_stats, coef_rename, model_parameters, extra_rows)
```


## Extensive margin

```{r}
get_f_stats <- function(model) {
  map(
    list(
      `F (2nd stage)` = fixest::fitstat(model, "f")$f$stat,
      `F (1st stage: high_share_tdif)` = fixest::fitstat(model, "ivf")$`ivf1::high_share_tdif`$stat),
    
    \(x) round(x, 4)
    )
}

# Rename coefficients
coef_rename <- c(
  "(Intercept)" = "Intercept",
  "x2" = "$\\frac{\\beta}{2}(h_{mt+1})^2$",
  "fit_high_share_tdif" = "Pasture Quality ($\\beta x_{mt+1} - x_{mt})$",
  "biomass_density" = "$b_m$",
  "year_tdif" = "$(\\beta + (\\beta - 1) t)$"
)

# Add model parameters as an extra column
model_parameters <- data.frame(
  "Parameters" = c(
  "\\Psi", "",
  "$\\delta$", "",
  "$\\gamma_{pasture}^e$", "",
  "$-\\alpha_b$", "",
  "$\\gamma_t^e$")
)

# Add controls, and F-statistics as extra rows
extra_rows <- data.frame(
  rowname = c("Controls", 
              "F (2nd stage)", 
              "F (1st stage: Past. Qual.)",
              "Clustered SE"),
  value = c(
    "Temp.; Past.Suit.; Mkt.Acc.",
    get_f_stats(ext_mod)[["F (2nd stage)"]],
    get_f_stats(ext_mod)[["F (1st stage: high_share_tdif)"]], 
    "Yes (Municipality)"),
  mod_par = ""
  )

# Name a model list dynamically 
header = paste0(
  "\\hline",
  "$ \\log \\left( \\frac{\\rho_{mt}}{1 - \\rho_{mt}} \\right)
    -\\beta \\log ( \\rho_{mt+1} ) + \\beta \\gamma $") 

model_list = setNames(list(ext_mod), header)

# Create the table
modelsummary(
  model_list,
  coef_map = coef_rename,
  gof_map = "nobs",
  fmt = 4, 
  statistic = "({std.error})", 
  stars = c("***"=0.01, "**"=0.05, "*"=0.10), 
  add_rows = extra_rows,
  title = "Extensive Margin OLS Regression Results\\label{tab:main_ext}",
  notes = paste(
    "Standard errors clustered at the municipality level.",
    "Controls: Pasture suitability, market access, 
      minimum, maximum, and mean temperature. All time varying controls have been calculated as an inter-temporal difference of the form $\\beta x_{mt+1}-x_{mt}$.",
    "Precipitation used as an instrument for pasture quality, also calculated as an inter-temporal difference."
  ),
  add_columns = model_parameters,
  output = "tinytable",
  escape = FALSE,
  width = 1
    ) |>
  style_tt(
    tabularray_inner = "
      rowsep = 4pt,
      row{1} = {valign = m},
      row{2,4,6,8} = {abovesep = 5pt, belowsep = -5pt}
      "
    ) |> 
  save_tt(
    output = "../Outputs/Tables/main_ext_table.tex",
    overwrite = T
  )

remove(get_f_stats, coef_rename, model_parameters, extra_rows, header, model_list)
```


## Structural parameters

In this section, I will use the preferred empirical exercise to recover the structural parameters that arise from the model.I first define a function to calculate the structural parameters, then run and export as latex table.

```{r}
calculate_structural_params <- function(int_model, ext_model) {
  # Extract coefficients and fixed effects from intensive margin
  int_coefs <- coef(int_model)
  int_fixed_effects <- fixef(int_model)$main_biome

  # Calculate intensive margin parameters
  alpha_p_delta <- - beta * int_coefs["fit_local_price"]
  phi <- (int_coefs["fit_local_price_2"] / alpha_p_delta) - 1

  # Extract coefficients and fixed effects from extensive margin
  ext_coefs <- coef(ext_model)

  # Calculate extensive margin parameters
  psi <- ext_coefs["(Intercept)"]
  delta <- ext_coefs["x2"]
  alpha_p <- alpha_p_delta * delta
  alpha_b <- - ext_coefs["biomass_density"]
  gamma_pasture_e <- ext_coefs["fit_high_share_tdif"]
  gamma_year_e <- - ext_coefs["year"]

  # Back to intensive margin
  gamma_pasture <- - int_coefs["fit_high_share"] * delta
  gamma_year <- - int_coefs["year"] * delta

  # fixed effects
  biomes = c(
    "amazonia", "caatinga", "cerrado", "mata atlantica", "pampa", "pantanal"
    )
  
  gamma_biome <- map_vec(int_fixed_effects, function(fe) - fe * delta) # multiply int mar FE by delta
  names(gamma_biome) <- paste("$\\gamma_g: g =$", biomes)
                        
  gamma_biome_e <- map_vec(ext_fixed_effects, function(fe) - fe)
  names(gamma_biome_e) <- paste("$\\gamma_g^e: g =$", biomes)
                          
  # Combine parameters into a data frame
  result <- data.frame(
    Parameter = c(
      "$\\phi$", "$\\delta$", "$\\alpha_p$", "$\\alpha_b$",
      "$\\gamma_{pasture}$", 
      "$\\gamma_t$",
      names(gamma_biome), 
      "$\\gamma_{pasture}^e$",
      "$\\gamma_t^e$",
      names(gamma_biome_e)
      ),
    
    Value = c(
      phi, delta, alpha_p, alpha_b,
      gamma_pasture, gamma_year,
      unname(gamma_biome), 
      gamma_pasture_e,
      gamma_year_e,
      unname(gamma_biome_e) 
      ),
    
    # Add column with parameters divided by alpha_p
    Scaled = c(
      NA,
      NA,
      NA,
      map_vec(c(alpha_b,
            gamma_pasture, gamma_year, unname(gamma_biome),
            gamma_pasture_e, gamma_year_e, unname(gamma_biome_e)),
          \(x) x / alpha_p)
      )
  )
  
  return(result)
}
```

Running the function.

```{r} 
calculate_structural_params(int_mod, ext_mod) |> 
  kbl(
    digits = c(4,4,2),
    
    # configure header
    col.names = c(
      paste0("\\hline", "\\addlinespace ",
        "Parameter"),
      "Value", 
      paste0("Scaled by $\\alpha_p$ (R\\$)",
             "\\vspace{0.4em}")
      ),
    
    booktabs = T,
    label = "tab:str_param",
    caption = "Structural Parameters",
    format = "latex",
    escape = FALSE,
    linesep = "\\addlinespace"
  ) |>
  kable_styling(
    full_width = T,
    htmltable_class =  "lightable-classic-2"
  ) |> 
  pack_rows("Intensive margin cost factors", 5, 12, latex_gap_space = "1em") |> 
  pack_rows("Extensive margin cost factors", 13, 20, latex_gap_space = "1em") |> 
  save_kable("../Outputs/Tables/str_param_table.tex")
```

## Extra tables

### First stage results

```{r}
coef_rename <- c(
  local_price = "$p_{mt}$",
  local_price_2 = "$p_{mt+1}$",
  high_share = "Pasture Quality",
  year = "Year",
  ssiv = "$ssiv_{mt}$",
  ssiv_2 = "$ssiv_{mt+1}$",
  pr = "Lag Precip",
  code_amc = "Municipality",
  main_biome = "Biome",
  biomass_density = "$b_m$",
  mata_atlantica = "mata atlantica",
  y = "$ \\log \\left( \\frac{\\rho_{mt}}{1 - \\rho_{mt}} \\right) -\\beta \\log ( \\rho_{mt+1} ) + \\beta \\gamma $",
  x2 = "$\\frac{\\beta}{2}(h_{mt+1})^2$",
  h = "$h_{mt+1}$"
  )

etable(
    int_mod,
    stage = 1,
    digits = 4,
    fitstat = ~ n + f + ivf,
    group = list(
      Temperature = c("tmmn_min", "tmmx_max", "tmmn_mean", "tmmx_mean"),
      `Past. Suit.` = "si_median",
      `Mkt. Acc.` = "ma_norm"
      ),
    dict = coef_rename,
    # output
    file = "../Outputs/Tables/int_first_stage.tex",
    replace = T,
    # latex configurations
    label = "tab:int_first_stage",
    tabular = "X",
    style.tex = style.tex(
      model.title = "",
      yesNo = "$\\checkmark$",
      fontsize = "normalsize",
      model.format = "\\hspace{1em}"
      ),
    title = "Intensive margin first stage results"
    )
```


### Fixed efects intensive margin

```{r}
etable(
    ols[[4]],
    stage = 2,
    digits = 4,
    fitstat = ~ n + f,
    group = list(
      Temperature = c("tmmn_min", "tmmx_max", "tmmn_mean", "tmmx_mean"),
      `Past. Suit.` = "si_median",
      `Mkt. Acc.` = "ma_norm"
      ),
    dict = coef_rename,
    # output
    file = "../Outputs/Tables/int_fe.tex",
    replace = T,
    # latex configurations
    label = "tab:int_fe",
    tabular = "X",
    style.tex = style.tex(
      model.title = "",
      yesNo = c("$\\checkmark$", "--"),
      fontsize = "normalsize",
      model.format = "\\hspace{1em}"
      ),
    title = "Intensive margin FE regression results"
    )
```


